---
title: 'Text Analysis: Frequencies'
author: "Niklas Cypris"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(quanteda)
library(quanteda.textplots)

theme_set(theme_classic())
```

```{r, warning=FALSE}
load("data/vid1.Rda")
load("data/vid2.Rda")
```

# Possible Analyses

# Meta Data

## Time of Publishing

```{r}

```

## Comments per User

```{r}

```

## Likes for Comments

```{r}

```

```{r}

```

## Replies to Posts

```{r}

```

# Exercise

Check out the meta data for the comments to the Oppenheimer movie.

# Textual Anaylsis

## Frequently-used Words

```{r}

```

```{r}

```

```{r}

```

*Remove special characters, keep emojis, and remove single letters:*

```{r}
pattern_to_remove <- "[^a-zA-Z0-9\\s\\x{1F600}-\\x{1F64F}\\x{1F300}-\\x{1F5FF}\\x{1F680}-\\x{1F6FF}\\x{1F700}-\\x{1F77F}\\x{1F780}-\\x{1F7FF}\\x{1F800}-\\x{1F8FF}\\x{1F900}-\\x{1F9FF}\\x{1FA00}-\\x{1FA6F}\\x{1FA70}-\\x{1FAFF}]|\\b[a-zA-Z]\\b"
```

**Special Letters**

The pattern "[^a-zA-Z0-9\\s]" matches any character that's not:
a lowercase letter (a-z)
an uppercase letter (A-Z)
a number (0-9)
or a whitespace (\\s)

**Emojis**

\x{1F600}-\x{1F64F} represents the range of emojis in the "emoticons" block of Unicode.

The other \x{...} ranges represent other blocks of emojis in the Unicode standard.

**Single Letters**

\\b[a-zA-Z]\\b matches single letters. Here, \\b is a word boundary anchor ensuring that it matches a single letter as a whole word.

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

## Wordcloud

```{r}

```

# Exercise

Apply the above-mentioned steps for the Oppenheimer movie data set. Which words are the most prominent words? Is there any overlap between movies? How about overlap in the 2grams?


# Further Reading

https://tutorials.quanteda.io/












