---
title: 'Youtube API: All'
author: "Niklas Cypris"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(tuber)
```

```{r, warning=FALSE}
source(file = "keys/auth.R")
```

# Video Information

```{r}
video_id <- ""
```

uYPbbksJxIg

pBk4NYhWNMM

## Statistics

```{r}
video_stats <- get_stats(video_id=video_id)
```

```{r}
video_stats %>% 
  as_tibble() %>% 
  type_convert()
```


## Information about the Video

```{r}
video_details <- get_video_details(video_id=video_id)
```

## Video Captions

```{r}
list_caption_tracks(
  part = "snippet",
  video_id = video_id)
```

```{r}
get_captions(id = "AUieDaZMZMD-xxuupVUD1Iaq2SCkFI3V6e2gW4WMYhpbOCDyG9k")
```

# Comments

```{r}
comment_threads <- get_comment_threads(c(video_id = video_id))
```

There are two tuber functions for collecting viewer comments for specific videos (both return a dataframe by default):

    get_comment_threads() collects comments for a video. By default, it collects the 100 most recent comments. The number of comments can be changed with the argument max_results (needs to be >= 20).

NB: If the number is > 100, the function should fetch all results (see ?get_comment_threads). However, the function has a bug, so that the resulting dataframe only contains repetitions of the 100 most recent comments when max_results > 100. Also, this function does not collect replies to comments. 

```{r}
all_comments <- get_all_comments(video_id = video_id)
```


    get_all_comments() collects all comments for a video, including replies to comments.

NB: This function only collects up to 5 replies per comment (the related issue in the tuber GitHub repo is still open). Depending on the number of comments for a video, running this function can take some time and might also deplete your API quota limit (more on that later).


```{r}
video_ids <- 
```

```{r}
multiple_vid_comments <- map_df(video_ids, get_all_comments)
```


# Other Stuff

Video search by keywords

All get commands:

1. Video
get_captions
get_stats
get_video_details
get_related_videos

2. Channel
get_all_channel_video_stats
get_channel_stats
get_subscriptions

3. Comments
get_all_comments
get_comments
get_comment_threads

4. Playlists
get_playlists
get_playlist_items












