---
title: 'Youtube API: All'
author: "Niklas Cypris"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(tuber)
```

```{r, warning=FALSE}
source(file = "keys/auth.R")
```

```{r}
yt_oauth(app_id =,
        app_secret = )
```


# Video Information

```{r}
video_id <- "pBk4NYhWNMM"
```

## Statistics

```{r}

```

```{r}

```


## Information about the Video

```{r}

```

# Comments

get_comment_threads():
The 100 most recent comments - can be changed with the argument max_results (>= 20).
Does not collect replies.

```{r}

```

get_all_comments():
All comments and the first five replies to each comment.

```{r}

```

# Exercise 1

Apply the steps for the following video: uYPbbksJxIg

Only looking at the comment texts, which video do you think you have downloaded?

# Exercise 2

Choose any video that you would like to look into and execute the steps.


# Other Stuff

Video search by keywords

All get commands:

1. Video
get_captions
get_stats
get_video_details
get_related_videos

2. Channel
get_all_channel_video_stats
get_channel_stats
get_subscriptions

3. Comments
get_all_comments
get_comments
get_comment_threads

4. Playlists
get_playlists
get_playlist_items
